---
title: "Functional groups"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, error=F, message = F)
pacman::p_load('dplyr', 'tidyr', 'gapminder', 'htmltools',
               'ggplot2',  'ggalt', 'ggmsa',
               'forcats', 'R.utils', 'png', 'BiocManager',
               'grid', 'ggpubr', 'scales', 'dendextend',
               'bbplot', 'data.table', 'dplyr', 'Biostrings', 'alakazam', "unikn", 
               'plotly', 'ggdendro', 'msa', 'msaR', 'DT', 'DECIPHER', "RColorBrewer")
```

```{r}
source("functions.R")
```

Summary statistics for each of the functional groups declared in the app.

The app includes the P1 and P11 naive datasets and the P4 non-naive dataset.

For P1 and P11 the following filtration criteria were applied:

* Functional sequence, no stop codons or frame shifts.
* Sequences which start from position 1 of the V gene.
* Sequences which didn't have gaps open (-) and didn't include any N's
* After changing into group annotations, sequences which had more than a single assignment in naive repertoires were remove.

The groups were created with similarity of 95% based on complete linkage and functional sequences and up to position 318.
